IGAS Project

### 2024-02-28 Sections/IGAS.qmd
re-render

```{r}
pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork)
source('Functions/IGAS_ProcessFunctions.R')

theme_set(theme_classic())
# load the processed data from experiment 1 and 2
e1 <- readRDS("data/igas_e1_cleanedData-final.rds")%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
e2<- readRDS('data/igas_e2_cleanedData-final.rds')%>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
e2_sim <- readRDS('data/IGAS_Similarity-Performance.rds')

@@

mf <- cowplot::ggdraw()+cowplot::draw_image("Assets/methodsFig1.png",hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
plot_grid(mf,ncol=1)

>>>>

```{r}
pacman::p_load(tidyr,papaja, knitr, tinytex, RColorBrewer, kableExtra, cowplot, patchwork,here)
source(here::here('Functions/IGAS_ProcessFunctions.R'))

theme_set(theme_classic())
# load the processed data from experiment 1 and 2
e1 <- readRDS(here::here("data/igas_e1_cleanedData-final.rds")) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity,stageInt=as.numeric(as.character(experimentStage)))
e2<- readRDS(here::here('data/igas_e2_cleanedData-final.rds')) %>% mutate(initialVelocityX=X_Velocity,initialVelocityY=Y_Velocity)
# load subject similarity data - computed with the IGAS model in 'IGAS-SimModel.R'
e2_sim <- readRDS(here::here('data/IGAS_Similarity-Performance.rds'))

@@

mf <- cowplot::ggdraw()+cowplot::draw_image(here::here("Assets/methodsFig1.png"),hjust=0)+theme(plot.margin = margin(0, 0, 0, 0))
plot_grid(mf,ncol=1)

### 2024-02-28 Sections/htw_exam.qmd
partial fix
re-render

---
# title: EXAM Fits and Predictions
date: last-modified
categories: [Simulation, ALM, EXAM, R]
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---

>>>>

---
# title: EXAM Fits and Predictions
# date: last-modified
# categories: [Simulation, ALM, EXAM, R]
code-fold: true
code-tools: true
execute: 
  warning: false
  eval: true
---
